### 2024-06-18 index.qmd
20240618 - buy coffee

```{=html}
<form action="https://www.paypal.com/donate" method="post" target="_top">
<input type="hidden" name="business" value="Q4FMMAMFQYTX8" />
<input type="hidden" name="no_recurring" value="0" />
<input type="hidden" name="item_name" value="Support me in developing this resource for fantasy football analytics... Even a cup of coffee ($4.99) helps me stay awake!" />
<input type="hidden" name="currency_code" value="USD" />
<input type="image" src="https://www.paypalobjects.com/en_US/i/btn/btn_donate_LG.gif" border="0" name="submit" title="PayPal - The safer, easier way to pay online!" alt="Donate with PayPal button" />
<img alt="" border="0" src="https://www.paypal.com/en_US/i/scr/pixel.gif" width="1" height="1" />
</form>
```

>>>>

```{=html}
<a href="https://www.buymeacoffee.com/isaactpetersen" target="_blank"><img src="https://cdn.buymeacoffee.com/buttons/v2/default-yellow.png" alt="Buy Me A Coffee" style="height: 60px !important;width: 217px !important;" ></a>

<script type="text/javascript" src="https://cdnjs.buymeacoffee.com/1.0.0/button.prod.min.js" data-name="bmc-button" data-slug="isaactpetersen" data-color="#FFDD00" data-emoji=""  data-font="Cookie" data-text="Buy me a coffee" data-outline-color="#000000" data-font-color="#000000" data-coffee-color="#ffffff" ></script>

<form action="https://www.paypal.com/donate" method="post" target="_top">
<input type="hidden" name="business" value="Q4FMMAMFQYTX8" />
<input type="hidden" name="no_recurring" value="0" />
<input type="hidden" name="item_name" value="Support me in developing this resource for fantasy football analytics... Even a cup of coffee ($4.99) helps me stay awake!" />
<input type="hidden" name="currency_code" value="USD" />
<input type="image" src="https://www.paypalobjects.com/en_US/i/btn/btn_donate_LG.gif" border="0" name="submit" title="PayPal - The safer, easier way to pay online!" alt="Donate with PayPal button" />
<img alt="" border="0" src="https://www.paypal.com/en_US/i/scr/pixel.gif" width="1" height="1" />
</form>
```
